\begin{thebibliography}{9}
\bibitem{csa}CSA Z662-11; Oil and gas pipeline systems - Sixth Edition; Update No. 1: January 2012
\bibitem{prci}Wang Y-Y.,et al (2011); “Second Generation Models for Strain-Based Design. Contract PR-ABD-1-Project 2. Final Approved Report Prepared for the Design, Materials and Construction Technical Committee of Pipeline Research Council International, (PRCI) Inc.
\bibitem{caminada}Caminada S, Cumino G, Cipolla L, Di Gianfrancesco, A (2009). “Cold bending of advanced ferritic steels: ASTM grades T23, T91, T92”. International Journal of Pressure Vessels and Piping 86 (2009) 853–861
\bibitem{das}Das, S. (2003): ``Fracture of Wrinkled Energy Pipelines'', Ph.D. dissertation, University of Alberta 
\bibitem{wang1}Wang Y-Y, Cheng W, Horsley D. (2004); “Tensile Strain Limits of Buried Defects in Pipeline Girth Welds” Proceedings of IPC2004, International Pipeline Conference, IPC2004-524
\bibitem{wang2}Wang Y-Y, Chen Y (2005); “Reliability Based Strain Design” Gas Research Institute Report 04/0146. Des Plaines, IL.
\bibitem{wang3}Wang Y-Y, Cheng W (2004); “Guidelines on Tensile Strain Limits” Gas Research Institute Report 04/0030. Des Plaines, IL.
\bibitem{wang4}Wang Y-Y, et al (2004); “Tensile Strain Limits of Girth Welds with Surface-Breaking Defects, Part 1 – An Analytical Framework” Proceedings of the 4th International Conference on Pipeline Technology, 235—249
\bibitem{wang5}Wang Y-Y, et al (2004); “Tensile Strain Limits of Girth Welds with Surface-Breaking Defects, Part 2 – Experimental Correlation and Validation” Proceedings of the 4th International Conference on Pipeline Technology, 251 – 266
\bibitem{montgomery}Montgomery D.C. (2009); “Design and Analysis of Experiments (7th Edition)”
\bibitem{sen1}Sen, M. (2006); “Behaviour of Cold Bend Pipes Under Combined Loads” Ph.D. dissertation, University of Alberta
\bibitem{sen2}Sen, M. , Cheng, J.J.R. , Zhou, J. (2011) ; “ Behaviour of Cold Bend Pipes under Bending Loads” 
DOI: 10.1061/(ASCE)ST.1943-541X.0000219. 2011 American Society of Civil Engineers
\bibitem{sen3}Sen, M. , Cheng, J.J.R. , Murray, D. W. (2004) ; “Full-Scale Tests of Cold Bend Pipes” Proceedings of IPC2004, International Pipeline Conference, IPC2004 – 743
\bibitem{miki}Miki, C. , Kobayashi, T. , Oguchi, N. , Uchida, T. , Suganuma, A. , Katoh, A. (2000) ; “Deformation and Fracture Properties of Steel Pipe Bend with Internal Pressure Subjected to In-Plane Bending”, Proceedings of the 12th World Conference on Earthquake Engineering
\bibitem{appSteel}Spiegel, L., Limbrunner, G.F. (1986); “Applied Structural Steel Design” 
\end{thebibliography}